Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-04 Manuscript Analyses/manuscript_analysis.Rmd
Knit draft rmd report

---
title: Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older
  Adult Listeners
author: "Lansford, Hirsch, Barrett, & Borrie"
date: "`r Sys.Date()`"
output: 
  github_document:
    code_folding: hide
    toc: true
    toc_float: true
---

>>>>

---
title: Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older
  Adult Listeners
author: "Lansford, Hirsch, Barrett, & Borrie"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---
